An Embedding Framework for Consistent Polyhedral Surrogates

### 2022-05-23 poly-embed-journal/poly-embed-journal.tex
meeting notes

The proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} uses a construction via convex conjugate duality which has appeared in several different forms in the literature (e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
We then apply a result we will prove in \S~\ref{sec:min-rep-sets}: a minimizable surrogate embeds a discrete loss if and only if their Bayes risks match (Proposition~\ref{prop:embed-bayes-risks}).

@@

Moreover, as we illustrate in Figure~\ref{fig:abstain-links}(L), the link $\psi^{\infty}$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ for any sufficiently small choice of $\epsilon > 0$.
Hence, our framework could have simplified the process of finding $\psi^\infty$, and the corresponding proof of consistency and surrogate regret bounds (\S~\ref{subsec:regret-bounds}\raft{check whether our bounds match}).
To illustrate this point further, we give an alternate link $\psi^1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R),
\begin{equation}\label{eq:abstain-link-1}
  \psi^1(u) = \begin{cases}
	\bot & \|u\|_1 \leq 1\\
	\varphi^{-1}(\sgn(u)) &\text{otherwise}
  \end{cases}~.
\end{equation}
Construction~\ref{const:eps-thick-link} gives calibration of $(L,\psi^1)$ with respect to $\ell$. 
Aside from its simplicity, one possible advantage of $\psi^1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right? EDIT 3/16/2022: if we add surrogate regret bounds to the paper, I think it could be fun and worth working out which link actually gives the better bound, at least from our best analysis.}

>>>>

The proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} uses a construction via convex conjugate duality which has appeared in several different forms in the literature (e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
\raft{Let's give a whole paragraph here, going into more detail about the results in these papers.  For reference on the style one could use here, see the paragraph after Theorem 3 of \url{https://arxiv.org/pdf/1506.07212.pdf}, the one starting ``We briefly mention various forms of Theorem 3 which have appeared in the literature.''.  To add: that top-k reviewer's reference.  I also think this paper of Bob's is relevant \url{https://icml.cc/2012/papers/367.pdf}; their definition of ``canonical link'' (which he mentioned in your defense BTW) maps target reports to subgradients of the Bayes risk, and in their continuous setting I think it's the same thing.}
We then apply a result we will prove in \S~\ref{sec:min-rep-sets}: a minimizable surrogate embeds a discrete loss if and only if their Bayes risks match (Proposition~\ref{prop:embed-bayes-risks}).

@@

Moreover, as we illustrate in Figure~\ref{fig:abstain-links}(L), the link $\psi^{\infty}$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ for any sufficiently small choice of $\epsilon > 0$.
Hence, our framework could have simplified the process of finding $\psi^\infty$, and the corresponding proof of consistency and surrogate regret bounds (\S~\ref{subsec:regret-bounds}\raft{let's reference the appendix where we derive the bound here}).
To illustrate this point further, we give an alternate link $\psi^1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R),
\begin{equation}\label{eq:abstain-link-1}
  \psi^1(u) = \begin{cases}
	\bot & \|u\|_1 \leq 1\\
	\varphi^{-1}(\sgn(u)) &\text{otherwise}
  \end{cases}~.
\end{equation}
Construction~\ref{const:eps-thick-link} gives calibration of $(L,\psi^1)$ with respect to $\ell$. 
Aside from its simplicity, one possible advantage of $\psi^1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right? EDIT 3/16/2022: if we add surrogate regret bounds to the paper, I think it could be fun and worth working out which link actually gives the better bound, at least from our best analysis.}
